\subsubsection{Chat Ops - sqrbot}
\label{sec:chatops}
%WOM Should this be title SQLBOT ? the tile does not mean much

DM-SQuaRE is using a Slack chatbot called ``sqrbot'' to make some tasks
easier. Currently it performs a range of functions, from returning the
status of various infrastructure machines to creating technotes to
monitoring whether metrics in our processing stack have changed between
CI builds; it also listens for mentions of Jira tickets, and when it
hears one, posts a link to that ticket.

All of these tasks are frequently requested actions that formerly
required breaking workflow.  Either (as with technote creation) the
requestor would have to interrupt someone else in order to get the work
performed, or they'd have to interrupt their own workflow to, for
instance, copy the ticket name, go to Jira, and search for the ticket.
With sqrbot, the requestor can simply ask sqrbot in a Slack channel for
the information (or creation of a technote skeleton, etc.) and get
immediate gratification without needing to task-switch or interrupt
a co-worker.

The basic architecture is simple: sqrbot is a collection of hubot
scripts running as a Slack bot, which in turn drive microservices,
written in Python and implemented using the Flask framework.  These
microservices have an API that responds with JSON, so the job of sqrbot
is simply to accept commands, create appropriate HTTP transactions, and
then reformat the output into a conversational format.  The whole
assembly runs in a Kubernetes cluster.
