\documentclass[]{spie}  %>>> use for US letter paper
%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing

\def\procspie{Proc.\ SPIE} % Proceedings of the SPIE

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{LSST Data Management Software Development Practices and Tools}

\author[a]{Tim~Jenness}
\author[a]{Frossie~Economou}
\author[b]{Krzysztof~Findeisen}
\author[c]{Fabio~Hernandez}
\author[a]{Josh~Hoblitt}
\author[a]{K.~Simon~Krughoff}
\author[d]{Kian-Tat~Lim}
\author[e]{Robert~H.~Lupton}
\author[d]{Fritz~Mueller}
\author[a]{William~O'Mullane}
\author[b]{Russell~Owen}
\author[f]{Stephen~R.~Pietrowicz}
\author[e]{Pim~Schellart}
\author[a]{Jonathan~Sick}
\author[b]{John~Swinbank}
\author[a]{Adam~Thornton}
\author[a]{Jeffrey~Kantor}
\author[b]{John~K.~Parejko}
\author[e]{Paul~Price}


\affil[a]{LSST Project Office, 950 N.\ Cherry Avenue, Tucson, AZ 85719, USA}
\affil[b]{University of Washington, Dept.\ of Astronomy, Box 351580, Seattle, WA 98195, USA}
\affil[c]{CNRS, CC-IN2P3, 21 avenue Pierre de Coubertin, CS70202, 69627 Villeurbanne cedex, France}
\affil[d]{SLAC National Accelerator Laboratory, 2575 Sand Hill Rd, Menlo Park, CA 94025, USA}
\affil[e]{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544}
\affil[f]{NCSA, University of Illinois at Urbana-Champaign, 1205 W.\ Clark St.\ Urbana, IL 61801}



\authorinfo{Further author information: (Send correspondence to T.J.)\\T.J.: E-mail: tjenness@lsst.org,\\  W.O'M: E-mail: womullan@lsst.org}

% Option to view page numbers
\pagestyle{empty} % change to \pagestyle{plain} for page numbers
\setcounter{page}{1} % Set start page numbering at e.g. 301

\begin{document}
\maketitle

\begin{abstract}
The Large Synoptic Survey Telescope (LSST) is an 8.4m optical survey telescope being constructed on Cerro Pach\'on in Chile.
The data management system being developed must be able to process the nightly alert data, 20,000 expected transient alerts per minute, in near real time, and construct annual data releases at the petabyte scale.
The development team consists of more than 90 people working in six different sites across the US developing an integrated set of software to meet the LSST requirements.
In this paper we discuss our agile software development methodology and our API and developer decision making process.
We also discuss the software tools that we use for continuous integration and deployment.
\end{abstract}

% Include a list of keywords after the abstract
\keywords{Agile Development, LSST, Distributed Development, Continuous Integration}


\input{intro}
\input{agile}
\input{mbse}
\input{software}
\input{comms}
\input{docs}
\input{rfc}
\input{ci}
\input{cd}
\input{conclusion}

\acknowledgments % equivalent to \section*{ACKNOWLEDGMENTS}

We thank all the people who have contributed to the tooling, processes, and discussions  over the years.
This material is based upon work supported in part by the National Science Foundation through Cooperative Agreement 1258333 managed by the Association of Universities for Research in Astronomy (AURA), and the Department of Energy under Contract No.\ DE-AC02-76SF00515 with the SLAC National Accelerator Laboratory.
Additional LSST funding comes from private donations, grants to universities, and in-kind support from LSSTC Institutional Members.
This work includes a contribution funded by France's CNRS / IN2P3 (Institut National de Physique Nucl\'{e}aire et de Physique des Particules).

% References
\bibliography{spie-10707-10} % bibliography data
\bibliographystyle{spiebib} % makes bibtex use spiebib.bst

\end{document}
